---
title: "Gap Minder"
output: html_document
---

The goal of this report is to analyze the data using `ggplot2`.



Here we have loaded the data and libraries to analyze the data.
```{r}
library(ggplot2)
library(dplyr)
gap.data.in <- read.delim("output//combined_gapMinder.tsv",header=TRUE,sep="\t")
names(gap.data.in)
```
Here we are subsetting three countries using 'dplyr'.
```{r}
angola <- filter(gap.data.in,country == "Angola")
pakistan <- filter(gap.data.in, country == "Pakistan")
argentina <- filter(gap.data.in, country == "Argentina")
all <- filter(gap.data.in, country=="Angola" | country=="Pakistan"| country=="Argentina")
```
Now we will plot GDP by year
First we will do some summary statistics on the dataset.
```{r}
ggplot(angola, aes(x=year,y=gdpPercap)) + geom_point() + geom_smooth()
ggplot(all, aes(x=year,y=gdpPercap,color=country)) + geom_point() + geom_smooth() 
```
Now we will get the mean, max and min of continents.
```{r}
asia <- filter(gap.data.in,continent=="Asia")
africa <- filter(gap.data.in,continent=="Africa")
americas <- filter(gap.data.in, continent=="Americas")
summary(asia$gdpPercap)
summary(africa$gdpPercap)
summary(americas$gdpPercap)
```

Next we would like to do three things:

1. Write this list
2. Do some stats
3. Make it look good

We could do this in any order

* This is one way
* Here is another